---
title: "Stackoverflow Data Analysis"
output: html_notebook
---

First, we will load libraries and data sets from 2011-207.
```{r}
library(tidyverse)
library(ggrepel)
library(plotly)

# Loading data sets from 2011-2017
d11 = read.csv("2011sosr.csv", header = F)
d12 = read.csv("2012sosr.csv", header = F)
d13 = read.csv("2013sosr.csv", header = F)
d14 = read.csv("2014sosr.csv", header = F)
d15 = read.csv("2015sosr.csv", header = F)
d16 = read.csv("2016sosr.csv", header = F)
d17 = read.csv("2017sosr.csv", header = F)
```


We will be using these to functions. The functions make a piechart for each year (2011-2017) of distribution of:

* occupation of Stackoverflow users

* what programming languages Stackoverflow users can do

```{r}
distOcc = function(d, year){
  countries <- data.frame(unique(select(d, country), incomparables=FALSE)$country)
  colnames(countries) <- "country"
  countries <- filter(countries, country != "")
  occ <- data.frame(unique(select(d, occupation), incomparables= FALSE))
  occ <- filter(occ, occupation != "")
  
  for(c in countries$country){
    occ[c] <- NA
  }
  
  # A list of occupations
  oc_list = c()
  for(c in occ$occupation){
    oc_list = c(oc_list, c)
  }
  
  # fill out all number of occupations for each country
  for(k in 1:length(oc_list)){
    for(i in 2:length(occ[1,])){
      occ[k,i] <- nrow(filter(filter(d, country==countries$country[i-1]), occupation==oc_list[k]))
    }
  }
  
  occ["SumCountries"] <- NA
  for(i in 2:20){
    for(k in 1:length(oc_list)){
      occ$SumCountries[k] <- rowSums(filter(occ, occupation==oc_list[k])[2:20])
    }
  }
  
  pie(occ$SumCountries, labels = oc_list, main=paste(c("Pie Chart of occupations (", year, ")"), collapse=""))
}




distLanguage = function(d, year){
  #ldf <- data.frame(d[1,c(4:length(d))])
  languages <- colnames(d[4:length(d)])
  val_list = c(1:length(languages))
  for(i in 1:length(languages)){
    val_list[i] <- sum(d==languages[i])
  }
  pie(x=val_list, labels=languages, main=paste(c("Distribution of \"do\" programming languages (", year, ")"), collapse=""))
}

```

For each data set we clean up and take out what we think are interesting.

# 2011
```{r}
d11 <- d11[-c(1,2),c(1,3,7,31:41)]
colnames(d11) = c("country","age","occupation","Java","JavaScript","CSS","PHP","Python","Ruby","SQL","C#","C++","C","Perl")
distOcc(d11, 2011)
```
```{r}
distLanguage(d11, 2011)
```

# 2012
```{r}
d12 <- d12[-c(1,2),c(1,3,7,23:35)]
colnames(d12) = c("country","age","occupation","Java","JavaScript","CSS","PHP","Python","Objective-C","Ruby","SQL","C#","C++","C","Perl", "HTML5")
distOcc(d12, 2012)
```

```{r}
distLanguage(d12, 2012)
```



# 2013
```{r}
d13 <- d13[-c(1,2),c(1,3,7,57:62,64:69)]
colnames(d13) = c("country","age","occupation","C","C++","C#","Java","JavaScript","jQuery","Node.js","Objective-C","PHP","Python","Ruby","SQL")
distOcc(d13, 2013)
```

```{r}
distLanguage(d13, 2013)
```



# 2014
```{r}
d14 <- d14[-c(1,2),c(1,4,7,43:53,56:65)]
colnames(d14) = c("country","age","occupation","C","C++","C#","Java","JavaScript","Node.js","Objective-C","PHP","Python","Ruby","SQL", "Haskell","CoffeeScript","Dart","C++11","redis","MongoDB","F#","Go","Hadoop","AngularJS")
distOcc(d14, 2014)
```

```{r}
distLanguage(d14, 2014)
```



# 2015
```{r}
d15 <- d15[-c(1,2),c(1,2,6,11:15,17,23,27:29,31:33,35:39,45,50)]
colnames(d15) = c("country","age","occupation","AngularJS","C","C++","C++11","C#","CoffeeScript","Go","Java","JavaScript","LAMP","MongoDB","Node.js","Objective-C","PHP","Python","R","Redis","Ruby","SQL","Wordpress")
distOcc(d15, 2015)
```

```{r}
distLanguage(d15, 2015)
```

The data sets from 2016 and 2017 has a major different structure, so we will only we looking at the distribution of occupations for these two years and not what programming languages Stackoverflow users can do.

# 2016
```{r}
d16 <- d16[-c(1,2),c(3,10)]
colnames(d16) = c("country","occupation")
distOcc(d16, 2016)
```


# 2017
```{r}
d17 <- d17[-c(1,2),c(4,16)]
colnames(d17) = c("country", "occupation")
distOcc(d17, 2017)
```